The Legacy of the European Post-Master in Urbanism at TU Delft: A Text Mining Approach

### 2023-02-19 analysis/paper/paper.qmd
Add comments and adjust topic model text

Similar to topic clustering on numeric data, topic modeling is a method of unsupervised classification of topics found in a group of documents [@silge2017].

```{r}
emu_theses_dtm <- emu_theses_words |> 
  count(title, word, sort = TRUE) |> 
  cast_dtm(title, word, n)

@@

emu_theses_lda <- LDA(emu_theses_dtm, k = 2, control = list(seed = 2023))
emu_theses_lda

emu_theses_topics <- tidy(emu_theses_lda, matrix = "beta")
emu_theses_topics

>>>>

Similar to clustering on numeric data, topic modeling is a method of unsupervised classification of topics found in a group of documents [@silge2017].

```{r}
# The topicmodels package requires a document-term matrix as input
emu_theses_dtm <- emu_theses_words |> 
  count(title, word, sort = TRUE) |> 
  cast_dtm(title, word, n)

@@

# We will use the Latent Dirichlet Allocation (LDA) algorithm for topic modeling
# In LDA, each document is a mixture of topics and each topic is a mixture of words
emu_theses_lda <- LDA(emu_theses_dtm, k = 2, control = list(seed = 2023))
emu_theses_lda

# 
emu_theses_topics <- tidy(emu_theses_lda, matrix = "beta")
emu_theses_topics
